<!-- 

3 Results  results.qmd

You have a lot of freedom to choose what to do, as long as you restrict yourselves to exploratory techniques (rather than modeling / prediction approaches). In addition, your analysis must be clearly documented and reproducible.

Provide a short nontechnical summary of the most revealing findings of your analysis written for a nontechnical audience. Take extra care to clean up your graphs, ensuring that best practices for presentation are followed, as described in the  audience ready style section  below.

Use subheadings (##) as appropriate. See  Todd Schneider’s blog posts  for examples of thoughtful, informative subheadings. An approach that works well is to create a subheading for each of your research questions.

The number of graphs will vary by project; we suggest a target of 10. (A plot with multiple facets counts as 1 graph).  If you go over, make sure they are high quality and include commentary.  A project with 10 good graphs plus commentary will receive a better grade than a project with 10 good graphs and 10 mediocre ones.
 -->

# Results

## Summary of findings


In the next few subsections, we dive into the details of how we drew these conclusions.

## Data pre-processing
To conduct deeper analysis on our data, we added the following columns to our dataset:

1. `BMI`: the Body Mass Index of each person, a continuous variable calculated using the [World Health Organization guideline](https://www.who.int/data/gho/data/themes/topics/topic-details/GHO/body-mass-index): $BMI = \frac{Weight}{Height^2}$.

2. `IsOverweight`: a binary categorical value whose value is 1 if the `BMI` of the person is more than 25, 0 otherwise.

These columns serve as alternate metrics of the obesity of an individual, a **continuous variable** and a **binary categorical variable**, to complement `NObeyesdad`, the obesity category level which is a **ordinal categorical variable**.

These new columns can be found and used directly in the dataset `materials/CleanObesityDataSet.csv`.

In order to improve the visualization of certain plots, we also made local modifications to the data types of some columns, as follows:

1. Rounded the variables: Frequency of consumption of vegetables (`FCVC`), Number of main meals (`NCP`), Physical activity frequency (`FAF`), Time using technology devices (`TUE`) 

## Analysis of Height, Weight and BMI variables
Since the dataset contains artificially generated data, we first needed to verify that the dataset matches our expectations, notably by visualizing the distribution of these three continuous variables.

Importing the necessary libraries and dataset
```{r setup, echo = T, results = 'hide', error=FALSE, warning=FALSE, message=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(stats)
library(vcd)
library(ggplot2)
library(gridExtra)
library(grid)
library(GGally)

data <- read_csv('materials/CleanObesityDataSet.csv',show_col_types = FALSE)
```

Preliminary verifications of the number of rows, columns and missing values of our dataset show that there does not seem to be any problems with the structure of our dataset.

```{r summary}
cat("Number of rows in dataset: ", nrow(data), "\nNumber of columns in dataset: ", ncol(data),"\nNumber of missing values in dataset: ", sum(is.na(data)))
```

Additionally, the data seems to align with our expectations, visualizing the `Height`, `Weight` and `BMI` variables shows that there are no biases with respect to the people surveyed.

```{r histogram}
# Histograms of Height, Weight and BMI

plot1 <- ggplot(data = data, aes(x = Height)) + geom_histogram(binwidth = 0.02)
plot2 <- ggplot(data = data, aes(x = Weight)) + geom_histogram(binwidth = 2)
plot3 <- ggplot(data = data, aes(x = BMI)) + geom_histogram(binwidth = 1)
grid.arrange(plot1, plot2, plot3, ncol = 3,
     top = textGrob("Histograms of the continuous variables Height, Weight and BMI",gp=gpar(fontsize=16)))

```

```{r shapiro tests, fig.width = 10}
shapiro.test(data$Height)
shapiro.test(data$Weight)
shapiro.test(data$BMI)
```

```{r qqplot, fig.width = 15}
plot1 <- ggplot(data, aes(sample = Height)) + 
  stat_qq() + 
  stat_qq_line(col = "navy") +
  xlab("Height")

plot2 <- ggplot(data, aes(sample = Weight)) + 
  stat_qq() + 
  stat_qq_line(col = "navy") +
  xlab("Weight")

plot3 <- ggplot(data, aes(sample = BMI)) + 
  stat_qq() + 
  stat_qq_line(col = "navy") +
  xlab("BMI")

grid.arrange(plot1, plot2, plot3, ncol = 3)

```


Analysis: 

On the histogram, it is not possible to tell for all three continuous variables whether they follow a normal 

1. The height of the individuals appears to follow a normal distribution, which is aligned with our expectations as it is an [assumption that researchers typically make](https://www.researchgate.net/figure/An-example-of-a-normal-distribution-height-distributions_fig1_264533994). 

2. The weight of the individuals does not appear to be normally distribution as it has a right skew. Body weight is found to have a right skew [according to research](https://pubmed.ncbi.nlm.nih.gov/11673780/#:~:text=Body%20weight%20is%20not%20normally,off%20of%20%2B0.5%20standard%20deviations.).

3. The BMI of individuals 


Lastly, we plotted a boxplot to better understand the other statistics (e.g. median, outliers) of the variable `BMI`.
```{r boxplot}
# Boxplot to visualize the BMI across all individuals 
ggplot(data, aes(x=BMI)) + 
  geom_boxplot(fill = "lightblue", color = "black") + 
  coord_cartesian(ylim = c(-2, 2)) +  
  labs(title = "Boxplot of BMI across all individuals")

fivenum(data$BMI)

```

[](materials/3_histograms.png)

[](materials/2_boxplot_bmi.png)



## Preliminary visualizations
```{r scatterplot, fig.width = 20, fig.height = 20}
set.seed(123456)

data <- data %>%
 mutate_if(is.numeric, scale)

data_num <- data[c("Age", "Height", "Weight", "NCP", "CH2O", "FAF", "TUE","BMI")]

# Convert all columns to numeric
data_num <- sapply(data_num, as.numeric)

# Sample 1000 points for clearer visualization
data_sampled <- sample_n(as.data.frame(data_num), 300)

ggpairs(as.data.frame(data_sampled), aes(alpha = 0.4, size = 0.02), 
           upper = list(continuous = wrap("cor", size = 12))) + 
  theme(text = element_text(size = 35))
```

## Understanding the correlation between biological factor and obesity 

## Correlation between lifestyle habits and obesity

<style>
    body {
        text-align: justify
    }
</style>

